Timely Object Detection

### 2012-02-13 writeups/eccv12/eccv12.tex
meeting with mario

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}

% Command definitions
\def\subsectionautorefname{section}
\definecolor{light-gray}{gray}{0.3}
\newcommand{\aside}[1]{\textcolor{light-gray}{\emph{#1}}}
\newcommand{\comment}[1]{}

@@

@@

The multi-class, multi-label \emph{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $i$, for each class $i \in \{1,\dots,K\}$.
The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(I,i)$.
We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_i$ is a $\{0/1\}$ binary variable set to $1$ if an object of class $i$ is present.
Henceforth we write $P(C_i)$ to mean $P(C_i=1)$, as shorthand.

@@

Our goal is a multi-class classification policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(C_1), \dots, \emph{classify}(C_K)\}$, where we omit the obvious dependency on $\mathcal{I}$.
The policy repeatedly selects an action $a$ from a set of actions $\mathcal{A}$, executes it, potentially receiving a set of observations, and selects the next action.
A dynamic (or ``closed-loop'') policy bases action selection on observations received from previous actions, allowing context to play a large role.
This sets our problem formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001}.

The set of actions $\mathcal{A}$ can include per-class classifiers, ``scene context'' functions, and feature computations.
For simplicity of exposition, let $\mathcal{A}$ consist of $2$ feature computations $F$ and $2K$ per-class classifiers $L$:
\begin{itemize}
	\item $L^\text{co}$ are one-vs-all SVMs on a complex featurization of the image (computed by $F^\text{co}$);
	\item $L^\text{sc}$ are SVMs on a simple scene-level feature (computed by $F^\text{sc}$).
\end{itemize}

@@

The system is given two times: the setup time $T_s$ and deadline $T_d$.
Between these times, the system must meet the goal of \emph{Anytime} performance and give the best possible answer at any point.

\begin{figure}[h!]
\center{\includegraphics[width=0.66\linewidth]
    {figures/evaluation.pdf}}
  \caption{\label{fig:evaluation}Our objective is to obtain \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time to deadline.}
\end{figure}

@@

In the language of decision processes, we define the \emph{state} of the decision process by the setting of $\mathbf{C}$ (the $K$ object presence variables $C_i$) and the time into episode $t$.
When the state has all the necessary information to make optimal action selections, the problem can be formalized as a Markov Decision Process.
Obviously, the true value of $\mathbf{C}$ is unknown to our system, so we define a \emph{belief state} $b$ as a distribution over states.
The belief state consists of the distribution $P(\mathbf{C}) = P(C_1, \dots, C_K)$, as well as $t$, and other variables.

A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$ and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

@@

\subsection{Reward definition}
Optimal performance results from becoming maximally certain of the correct values of every $C_i$ as quickly as possible (given the setup time).
Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to an action taken in a belief state.
Let's say that given deadline $T_d$, the policy had time to take $J$ actions.
The total expected reward of a policy $\pi$ is then defined as the sum of rewards
\begin{equation}
\mathbb{E}_\pi[\sum_{j=0}^J R(b_j, a_j)]
\end{equation}
We explore two options for the reward function: the first is derived directly from the evaluation metric; the second cares only about entropy of $P(\mathbf{C})$.

\subsubsection{Slope of performance vs. time}
Remembering that the final evaluation of a policy consists of the area under the performance vs. time curve, we formulate a per-action reward such that the addition of

\subsubsection{Information gain}

\subsection{Learning the value of an action}
At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{subfig}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}

% Definitions
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\def\subsectionautorefname{section}
\definecolor{light-gray}{gray}{0.3}
\newcommand{\aside}[1]{\textcolor{light-gray}{\emph{#1}}}
\newcommand{\todo}[1]{\textcolor{red}{\emph{#1}}}
\newcommand{\comment}[1]{}

@@

\subsection{Problem Setting} \label{sec:problem_setting}

@@

The multi-class, multi-label \emph{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $i$, for each class $i \in \{1,\dots,K\}$.
The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},i)$.
We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_i \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $i$ is present.

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.66\linewidth]
    {figures/pomdp.pdf}}
  \caption{Summary of our approach to the problem. Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
  \label{fig:evaluation}
\end{figure}

Our goal is a multi-class classification policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$.
The policy repeatedly selects an action $a$ from a set of actions $\mathcal{A}$, executes it, potentially receives a set of observations, and selects the next action.
A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the classifiers.
This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or \todo{add another one}.

The set of actions $\mathcal{A}$ can include per-class classifiers, ``scene context'' functions, and feature computations.
For simplicity of exposition, let $\mathcal{A}$ consist of $K+1$ feature computations $F$ and $2K$ per-class classifiers $L$:
\begin{itemize}
	\item $L^\text{co}_i$ are one-vs-all SVMs on a complex featurization of the image (computed by $F^\text{co}_i$);
	\item $L^\text{sc}_i$ are SVMs on a simple scene-level feature (computed by $F^\text{sc}$).
\end{itemize}

\todo{
Consider revising the above to make a single action compute all the scene classifiers at once.
}

@@

The system is given two times: the setup time $T_s$ and deadline $T_d$.
Between these times, the system must meet the goal of \emph{Anytime} performance and give the best possible answer to the classification problem at any point.

\begin{figure}[h!]
\center{\includegraphics[width=0.66\linewidth]
    {figures/evaluation.pdf}}
  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
  \label{fig:evaluation}
\end{figure}

@@

We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, and other variables that will be discussed in \autoref{sec:value}.
The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.

An action $a$ can result in a set of observations $o$ that can be used to update the belief state.
At the very least, the state records the fact that $a$ has been taken.
A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

The policy's performance is determined by treating the final values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ for the multi-label classification evaluation (see \autoref{sec:problem_setting}).

@@

\subsection{Reward} \label{sec:reward}
The goal of our policy is Anytime performance, so it would be limiting to evaluate only at deadline time.
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to an action taken in a belief state.

Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total expected reward of a policy $\pi$ is then defined as the sum of rewards
\begin{equation}
\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
\end{equation}

The reward function does not necessarily have to be related to the evaluation of the system.
We explore two options for the reward function: the first is derived directly from the evaluation metric; the second seeks to minimize entropy of $P(\mathbf{C})$.

\subsubsection{Slope of performance vs. time}
\begin{figure}[htb]
  \center{\includegraphics[width=0.66\linewidth]{figures/apvst_expl.pdf}}
  \caption{\label{fig:rewards}A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action. The figure shows this analysis for the action highlighted in orange.}
\end{figure}

Remembering that the final evaluation of a policy consists of the area under the performance vs. time curve, we formulate per-action rewards such that their addition results in precisely this quantity.
Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
\Delta AP (t_T-\Delta t)
\end{equation}
where $t_T$ is the time left until deadline, and $\Delta t$ and $\Delta AP$ are the time taken and AP change produced by the action.

The equation breaks down into a term to maximize, $\Delta AP t_T$, and a term to minimize, $\Delta AP \Delta t$.
This agrees with the intuition that to capture the most area under the curve, the slope needs to be maximized at each point.
Additionally, the equation shows that if $\Delta t$ exceeds $t_T$, the value of taking the action is negative.

\subsubsection{Information gain}
A common approach to our kind of problem is to minimize uncertainty as quickly as possible.
Specifically,

\todo{What's the difference here between minimizing entropy and maximizing expected information gain over the length of the episode?}

\subsection{The value function} \label{sec:value}
At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
We therefore define our policy as
\begin{equation}
\argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
\end{equation}

Learning this accurately is the domain of Reinforcement Learning research, and is generally intractable for large-scale POMDPs.
We explore three different value functions.

First, we seek to maximize the expected next-stage reward, and manually construct a value function such that picking the action with maximal value achieves this.
Next, we note that the manually constructed value function can be represented as a scalar product of a parameter vector with a featurization of the belief state; we learn the weights by regression to the actual next-stage reward from running many episodes.
Lastly, we use a reinforcement learning technique to learn the weights such that the expected rewards over the whole episode are maximized.

\subsubsection{Manually specified greedy value function}

\subsubsection{Learning the greedy policy}

\subsubsection{Learning the proper policy}
\note{I'm considering two options here: (1) log-linear representation and policy gradient algorithm; (2) least-squares policy iteration.}

\paragraph{Policy gradient algorithm}
We redefine our policy as picking the mode of a log-linear parametrized distribution:
\begin{equation}
P(a|b;\theta) = \frac{\exp(\theta^T \phi(b,a))}{\sum_{a' \in \mathcal{A}} \exp(\theta^T \phi(b,a')}
\end{equation}

Basically stochastic gradient ascent on the estimate of the reward accrued by an episode.

This approach has been shown to scale to large problems in \cite{Branavan2009,Sutton2000}, although it has been proven to converge only to local maxima and only for MDPs.

\note{Does the constraint that no action is taken more than once affect this algorithm?}

\paragraph{Least-squares Policy Iteration}
An efficient form of temporal-difference learning used in \cite{Kwok2004}.
Policy remains parameterized as it was.

\subsection{Updating the belief state}
While the value function can learn certain dependencies between class occurrences, its job is made easier if the belief state already presents features that clearly present the relevant signals, such as co-occurence.
Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations.
It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.

We explore two alternatives for the inference model: a fully-connected Markov Random Field (MRF) and a locally weighted regression, as shown in Figure~\ref{fig:models}.

\begin{figure}[h!]
\centering
\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}} \hfill
\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
\caption{The models present a point in the middle of the decision process, when some classifiers have already been observed.}
\label{fig:models}
\end{figure}

\subsubsection{MRF inference}
Pros: (probably) more efficient at test time.

Cons: model too restrictive? not exact inference.

\subsubsection{Locally weighted regression}
Approach of \cite{Gao2011}.

Pros: imposing minimal model constraints (except Gaussian assumptions);

Cons: expensive at test time; data too sparse?
